Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2016-12-31 paper/ms.tex
merging

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/sho.pdf}
\includegraphics[width=0.5\textwidth]{figures/acf_sho.pdf}
\caption{(top) The power spectrum of a stochastically-driven simple harmonic
    oscillator (\eqalt{sho-psd}) plotted for several values of the quality
    factor $Q$.
    For comparison, the dashed line shows the Lorentzian function from
    \eq{lorentz-psd} with $c_j = 2\,Q = 20$ and normalized so that
    $S(d_j) = Q^2 = 100$. (bottom) The corresponding autocorrelation functions.
    \figurelabel{sho}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/sho.pdf}
\caption{(left) The power spectrum of a stochastically-driven simple harmonic
    oscillator (\eqalt{sho-psd}) plotted for several values of the quality
    factor $Q$.
    For comparison, the dashed line shows the Lorentzian function from
    \eq{lorentz-psd} with $c_j = 2\,Q = 20$ and normalized so that
    $S(d_j) = Q^2 = 100$.
    (right) The corresponding autocorrelation functions with the same colors.
    \figurelabel{sho}}
\end{center}
\end{figure}
